Stability concerns in random matrices

### 2018-04-15 ms.Rmd
Figure legend and sub-panel letters

**Figure 1**

```{r, eval = TRUE, echo = FALSE, fig.height = 8}
make_gammas <- function(nn = 10, distribution = 1, mn = 10, sdd = 1){
    if(distribution == 0){
        dat          <- rep(x = mn, times = nn);
    }
    if(distribution == 1){
        dat          <- rnorm(n = nn, mean = mn, sd = sdd);
        dat[dat < 0] <- -dat[dat < 0];
    }
    if(distribution == 2){
        dat          <- runif(n = nn, min = 0, max = 20);
        dat          <- sdd * ((dat - mean(dat)) / sd(dat));
        dat          <- dat + mn;
    }
    if(distribution == 3){
        dat          <- rexp(n = nn);
        dat          <- sdd * ((dat - mean(dat)) / sd(dat));
        dat          <- dat + mn;
    }
    if(distribution == 4){
        dat          <- 1 - (sdd * rexp(n = nn));
        dat          <- dat - min(dat);
        dat          <- dat - mean(dat) + mn;
        dat[dat < 0] <- -dat[dat < 0];
    }
    if(distribution == 5){
        dat          <- rbeta(n = nn, shape1 = 0.5, shape2 = 0.5);
        dat          <- sdd * ((dat - mean(dat)) / sd(dat));
        dat          <- dat + mn;
    }
    if(distribution == 6){
        dat          <- rgamma(n = nn, shape = 2, scale = 2);
        dat          <- sdd * ((dat - mean(dat)) / sd(dat));
        dat          <- dat + mn;
    }
    return(dat);
}
show_gammas <- function(nn = 1000000){
    y1 <- make_gammas(nn = nn, distribution = 1);
    y2 <- make_gammas(nn = nn, distribution = 2);
    y3 <- make_gammas(nn = nn, distribution = 3);
    y4 <- make_gammas(nn = nn, distribution = 4);
    y5 <- make_gammas(nn = nn, distribution = 5);
    y6 <- make_gammas(nn = nn, distribution = 6);
    par(mfrow = c(3, 2), oma = c(6, 6, 1, 1), mar = c(4, 0.5, 0.5, 0.5));
    hist(y1, breaks = 1000, yaxt = "n", main = "", xlab = "", cex.axis = 1.5);
    box();
    hist(y2, breaks = 1000, yaxt = "n", main = "", xlab = "", cex.axis = 1.5);
    box();
    hist(y3, breaks = 1000, yaxt = "n", main = "", xlab = "", cex.axis = 1.5);
    box();
    hist(y4, breaks = 1000, yaxt = "n", main = "", xlab = "", cex.axis = 1.5);
    box();
    hist(y5, breaks = 1000, yaxt = "n", main = "", xlab = "", cex.axis = 1.5);
    box();
    hist(y6, breaks = 1000, yaxt = "n", main = "", xlab = "", cex.axis = 1.5);
    box();
    mtext(expression(paste("Component ",gamma[i]," value")),
          outer=TRUE,side=1,line=3.0,cex=2);
    mtext(expression(paste("Relative frequency")),
          outer=TRUE,side=2,line=2.5,cex=2);
}
show_gammas();
```

>>>>

**Figure 1: Distributions of component response rate ($\boldsymbol{\gamma}$) values in complex systems. The stabilities of simulated complex systems with these $\gamma$ distributions are compared to otherwise identical complex systems with a fixed component response rate of $\boldsymbol{\gamma = 10}$ across different system sizes ($\boldsymbol{S}$; i.e., component numbers) and $\boldsymbol{\gamma}$ standard deviations ($\boldsymbol{\sigma_{\gamma} = \{1, 2, 4, 8\}}$). All distributions shown below are mean-centred at $\boldsymbol{\mu = 10}$. Distributions are as follows: (a) normal, (b) uniform, (c) exponential, (d) reversed exponential (built from 1 minus an exponential distribution, which is then mean-centred and standardised), beta ($\boldsymbol{\alpha = 0.5}$ and $\boldsymbol{\beta = 0.5}$), and gamma ($\boldsymbol{k = 2}$ and $\boldsymbol{\theta = 2}$). Each panel shows 1 million randomly generated \boldsymbol{$\gamma$} values.**

```{r, eval = TRUE, echo = FALSE, fig.height = 8}
make_gammas <- function(nn = 10, distribution = 1, mn = 10, sdd = 1){
    if(distribution == 0){
        dat          <- rep(x = mn, times = nn);
    }
    if(distribution == 1){
        dat          <- rnorm(n = nn, mean = mn, sd = sdd);
        dat[dat < 0] <- -dat[dat < 0];
    }
    if(distribution == 2){
        dat          <- runif(n = nn, min = 0, max = 20);
        dat          <- sdd * ((dat - mean(dat)) / sd(dat));
        dat          <- dat + mn;
    }
    if(distribution == 3){
        dat          <- rexp(n = nn);
        dat          <- sdd * ((dat - mean(dat)) / sd(dat));
        dat          <- dat + mn;
    }
    if(distribution == 4){
        dat          <- 1 - (sdd * rexp(n = nn));
        dat          <- dat - min(dat);
        dat          <- dat - mean(dat) + mn;
        dat[dat < 0] <- -dat[dat < 0];
    }
    if(distribution == 5){
        dat          <- rbeta(n = nn, shape1 = 0.5, shape2 = 0.5);
        dat          <- sdd * ((dat - mean(dat)) / sd(dat));
        dat          <- dat + mn;
    }
    if(distribution == 6){
        dat          <- rgamma(n = nn, shape = 2, scale = 2);
        dat          <- sdd * ((dat - mean(dat)) / sd(dat));
        dat          <- dat + mn;
    }
    return(dat);
}
show_gammas <- function(nn = 1000000){
    y1 <- make_gammas(nn = nn, distribution = 1);
    y2 <- make_gammas(nn = nn, distribution = 2);
    y3 <- make_gammas(nn = nn, distribution = 3);
    y4 <- make_gammas(nn = nn, distribution = 4);
    y5 <- make_gammas(nn = nn, distribution = 5);
    y6 <- make_gammas(nn = nn, distribution = 6);
    par(mfrow = c(3, 2), oma = c(6, 6, 1, 1), mar = c(4, 0.5, 0.5, 0.5));
    h1 <- hist(y1, breaks = 1000, plot = FALSE);
    hist(y1, breaks = 1000, yaxt = "n", main = "", xlab = "", cex.axis = 1.5,
         ylim = c(0, max(h1$counts)*1.2));
    mtext("a", adj = 0, line = -2.3, cex = 2, 
          at = par("usr")[1]+0.90*diff(par("usr")[1:2]));
    box();
    h2 <- hist(y2, breaks = 1000, plot = FALSE);
    hist(y2, breaks = 1000, yaxt = "n", main = "", xlab = "", cex.axis = 1.5,
         ylim = c(0, max(h2$counts)*1.2));
    mtext("b", adj = 0, line = -2.3, cex = 2, 
          at = par("usr")[1]+0.90*diff(par("usr")[1:2]));
    box();
    h3 <- hist(y3, breaks = 1000, plot = FALSE);
    hist(y3, breaks = 1000, yaxt = "n", main = "", xlab = "", cex.axis = 1.5,
         ylim = c(0, max(h3$counts)*1.2));
    mtext("c", adj = 0, line = -2.3, cex = 2, 
          at = par("usr")[1]+0.90*diff(par("usr")[1:2]));
    box();
    h4 <- hist(y4, breaks = 1000, plot = FALSE);
    hist(y4, breaks = 1000, yaxt = "n", main = "", xlab = "", cex.axis = 1.5,
         ylim = c(0, max(h4$counts)*1.2));
    mtext("d", adj = 0, line = -2.3, cex = 2, 
          at = par("usr")[1]+0.90*diff(par("usr")[1:2]));
    box();
    h5 <- hist(y5, breaks = 1000, plot = FALSE);
    hist(y5, breaks = 1000, yaxt = "n", main = "", xlab = "", cex.axis = 1.5,
         ylim = c(0, max(h5$counts)*1.2));
    mtext("e", adj = 0, line = -2.3, cex = 2, 
          at = par("usr")[1]+0.90*diff(par("usr")[1:2]));
    box();
    h6 <- hist(y6, breaks = 1000, plot = FALSE);
    hist(y6, breaks = 1000, yaxt = "n", main = "", xlab = "", cex.axis = 1.5,
         ylim = c(0, max(h6$counts)*1.2));
    mtext("f", adj = 0, line = -2.3, cex = 2, 
          at = par("usr")[1]+0.90*diff(par("usr")[1:2]));
    box();
    mtext(expression(paste("Component ",gamma," value")),
          outer=TRUE,side=1,line=3.0,cex=2);
    mtext(expression(paste("Relative frequency")),
          outer=TRUE,side=2,line=2.5,cex=2);
}
show_gammas();
```
